A comprehensive approach to analyzing environmental data with non-detects

### 2024-09-04 Rmarkdown/paper.Rmd
minor edits to manuscript

This work was supported by NSERC through an Alliance Grant (ALLRP 568507--21). We acknowledge Halifax Water staff for facilitating sample collection at the treatment facilities and Heather Daurie, Alyssa Chiasson, Evelyne Dor&eacute;, Jorginea Bonang, Genevieve Erjavec, Sebastian Munoz, and Bofu Li for laboratory assistance.

>>>>

This work was supported by NSERC through an Alliance Grant (ALLRP 568507--21). We acknowledge utility staff for facilitating sample collection at the treatment facilities and Heather Daurie, Alyssa Chiasson, Evelyne Dor&eacute;, Jorginea Bonang, Genevieve Erjavec, Sebastian Munoz, and Bofu Li for laboratory assistance.
